Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-26 manuscript/manuscript.Rmd
reworded math models a bit

In this section we introduce some models describing the population dynamics of fisheries.
In general, the class of models that appear in this context are *first order finite difference equations* (potentially stochastic difference equations).
For $n$ species, these models have the general form

\begin{align}
  \label{eq:general model}
  \Delta N_t := N_{t+1} - N_t = f(N_t) - F^T N_t,
\end{align}
where $N_t = (X_t,\ Y_t,\ \dots) \in \mathbb{R}^{n}_+$ is a vector of populations, $f:\mathbb{R}^{n}\to\mathbb{R}^{n}$ is an arbitrary function, where the product of the mortality and the stock size, $F^T N_t$ is the harvest size at timestep $t$. 
Here, $F\in\mathbb{R}^n$ is a vector of fishing intensities, where $F_i$ is the intensity with which the $i$-th species is fished.
We will focus on the case where only the first species is fished, $F= (F_1,\ 0,\ \dots,\ 0)$.

>>>>

In this section we introduce some models describing the population dynamics of fisheries.
In general, the class of models that appear in this context are *first order finite difference equations* (potentially stochastic difference equations).
For $n$ species, these models have the general form
\begin{align}
  \label{eq:general model}
  \begin{split}
    \Delta X_t &:= X_{t+1} - X_t = f_X(N_t) - M_X X_t\\
    \Delta Y_t &:= X_{t+1} - Y_t = f_Y(N_t) - M_Y Y_t\\
    &\dots
  \end{split}
\end{align}
where $N_t = (X_t,\ Y_t,\ \dots) \in \mathbb{R}^{n}_+$ is a vector of populations and $f_i:\mathbb{R}^{n}\to\mathbb{R}$ are arbitrary functions.
Here, $M_i=M_i(N_t)\in\mathbb{R}_+$ is a state-dependent fish mortality arising from harvesting (sometimes referred to as *fishing effort*).
Thus, the term $M_X X_t$ is the total $X$ harvest at time $t$.
We will focus on systems where a single species, $X$ is harvested, i.e. $M_Y = M_Z = \dots = 0$.
